### 2023-05-03 paper.Rmd
make contribution of simulation more clear

To thoroughly evaluate the k-plus approach to anticlustering, two specific k-plus criteria were compared to two traditional anticlustering criteria: (a) "standard" k-plus anticlustering, minimizing differences with regard to group means and variances (by maximizing $\mathit{SSE_{kplus}}$); (b) "generalized" k-plus anticlustering, minimizing differences with regard to group means, variances, skewness and kurtosis (by maximizing $\mathit{SSE_{kplusGeneralized}}$ with $T = 4$). To implement the k-plus objectives, the unweighted standardization approach was employed that performed best in Simulation 1. Thus, to optimize a k-plus criterion, the original data set was augmented to incorporate the additional criteria and all variables---the original and the augmented variables---were $z$-standardized. Subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set. The k-plus methods were compared to (i) k-means anticlustering, minimizing differences with regard to group means, (ii) diversity anticlustering, maximizing the sum of pairwise Euclidean distances within groups, (iii) a random allocation of elements to groups.

>>>>

In Simulation 2, the performance of two k-plus criteria was compared to the performance of two traditional anticlustering criteria. "Standard" k-plus anticlustering was implemented by maximizing $\mathit{SSE_{kplus}}$, thus minimizing differences with regard to group means and variances. "Generalized" k-plus anticlustering was implemented by maximizing $\mathit{SSE_{kplusGeneralized}}$ using $T = 4$, thus minimizing differences with regard to group means, variances, skewness and kurtosis. To implement the k-plus objectives, the unweighted standardization approach was employed that performed best in Simulation 1. Thus, to optimize a k-plus criterion, the original data set was augmented to incorporate the additional criteria and all variables---the original and the augmented variables---were $z$-standardized. Subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set. The k-plus methods were compared to (i) k-means anticlustering, minimizing differences with regard to group means, (ii) diversity anticlustering, maximizing the sum of pairwise Euclidean distances within groups, and also (iii) a random allocation of elements to groups.
